%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Experience}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}
    \cventry
    {Software Engineer}
    {IOTA Foundation}
    {Remote}
    {July 2020 - November 2020 \linebreak April 2021 - Present}
    {
        \begin{cvitems}
        \item Design and maintain \href{https://crates.io/crates/packable}{\underline{Packable}}, a \texttt{\#[no\_std]} binary serialization framework used by several Rust projects inside the foundation.
        \item Port and optimize the CurlP hashing algorithm to Rust.
        \item Debug several concurrency issues inside the \href{https://github.com/iotaledger/bee/}{\underline{Bee}} framework protocol.
        \end{cvitems}
    }
    \cventry
    {Full-time Professor}
    {Universidad Sergio Arboleda}
    {Bogotá, Colombia}
    {February 2020 - July 2020}
    {
        \begin{cvitems}
        \item In charge of the mainstreaming process for introductory Computer Science courses.
        \item Designed the syllabi for the courses on compilers and algorithm design for the new program in computer science.
        \end{cvitems}
    }
    \cventry
    {Contributor}
    {The Rust Compiler Project}
    {}
    {October 2017 - June 2020}
    {
        \begin{cvitems}
        \item Added support for Integer-Pointer casts in Miri to allow pointer arithmetic.
        \item Implemented distinct primitives for interpreter-host communication in Miri.
        \item Weakened several compiler checks to expand constant evaluation support.
        \end{cvitems}
    }
    \cventry
    {CMS Site Support Operator}
    {Fermi National Accelerator Laboratory}
    {Batavia, Illinois, United States}
    {June 2019 - November 2019}
    {
        \begin{cvitems}
        \item{Responsible for monitoring and troubleshooting all the services of the CMS distributed computing infrastructure.}
        \end{cvitems}
    }

    \cventry
    {Graduate Assistant}
    {Universidad de los Andes}
    {Bogotá, Colombia}
    {February 2018 - December 2018}
    {
        \begin{cvitems}
        \item{In charge of one section and two laboratories of the undergraduate course in discrete mathematics and logic.}
        \end{cvitems}
    }

    \cventry
    {Data Scientist} % Job title
    {Rappi inc.} % Organization
    {Bogotá, Colombia} % Location
    {June 2017 - March 2018} % Date(s)
    {
        \begin{cvitems}
        \item{Co-designer of the A / B testing platform used on the CPGs search engine.}
        \item{Introduced human search quality rating into the Quality Assurance process for the CPGs search engine.}
        \item{Developed a predictive model to estimate the time of payment of a debt acquired by a domiciliary.}
        \item{Developed a data pipeline to monitor the distribution of supply and demand in near real time.}
        \end{cvitems}
    } % Description(s) of tasks/responsibilities


    \cventry
    {Graduate Research Assistant} % Job title
    {Alianza CAOBA} % Organization
    {Bogotá, Colombia} % Location
    {July 2016 - August 2017} % Date(s)
    {
        \begin{cvitems}
        \item{Developed a web application to monitor the state of the public transport service in Rio de Janeiro.}
        \item{Study on traffic and mobility in order to characterize traffic accidents in Bogotá.}
        \item{Study on taxes of urban delineation and characterization of taxpayers in order to detect anomalous \\declarations of constructions in Bogotá.}
        \end{cvitems}
    } % Description(s) of tasks/responsibilities


    \vspace{-0.5cm}
\end{cventries}
