%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Programming}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cvskills}

%------------------------------------------------

\cvskill
{C} % Category
{
  \begin{cvitems}
  \item {Mainly for optimizing specific tasks in scientific programming.}
  \item {Experience writing Python modules over CPython.}
  \end{cvitems}
}

%------------------------------------------------

\cvskill
{Elixir} % Category
{
  \begin{cvitems}
  \item {As a general purpose programming language.}
  \item {Experience writing concurrent applications using OTP.}
  \item {Experience using Plug for backend web development.}
  \item {Some experience writing ETL tools.}
  \end{cvitems}
}

%%------------------------------------------------

\cvskill
{Go} % Category
{
  \begin{cvitems}
  \item {As a fast development programming language.}
  \item {Experience developing web applications using Echo and Gorilla/Mux.} 
  \end{cvitems}
}

%------------------------------------------------

\cvskill
{Java} % Category
{
  \begin{cvitems}
  \item {As a general purpose programming language.}
  \item {Some experience using Hadoop for data processing.}
  \end{cvitems}
}

%------------------------------------------------

\cvskill
{Javascript} % Category
{
  \begin{cvitems}
  \item {Experience using ReactJS for frontend web development.}
  \item {Developed interactive dashboards for near real-time monitoring.}
  \item {Basic knowledge of D3.js for Data visualization.}
  \end{cvitems}
}

%------------------------------------------------

\cvskill
{Python} % Category
{
  \begin{cvitems}
  \item {As a general purpose programming language.}
  \item {Experience using Numpy, Pandas and PySpark for data processing.}
  \item {Experience using Scikit-learn and Tensorflow for machine learning.}
  \item {Experience using Flask and Tornado for backend web development.}
  \end{cvitems}
}

%------------------------------------------------

\cvskill
{Rust} % Category
{
  \begin{cvitems}
  \item {For Systems Programming in several contexts.}
  \item {Experience developing basic web applications.}
  \item {Experience writing embeddable modules for Python.}
  \item {Done small contributions to Rust related projects like Servo, Cargo and Rust itself.}
  \item {Mentor of the Rust track in exercism.io}
  \end{cvitems}
}

%------------------------------------------------

\cvskill
{Others} % Category
{
  \begin{cvitems}
  \item {Experience using Git for VCS.}
  \item {Experience using Docker to deploy microservices and other applications.}
  \item {Experience using Redis for real-time data processing.}
  \item {Experience using PostgreSQL.}
  \item {Experience using MongoDB including its geospatial features.}
  \item {Experience using InfluxDB and connecting it with Grafana for time series analytics.}
  \item {Proud Linux user since 2010.}
  \end{cvitems}
}

%------------------------------------------------

\end{cvskills}
